### 2015-06-05 Code/Docs/paper.tex
doc added

%\documentclass[9pt,twocolumn]{IEEEtran}
%\documentclass[12pt,twoside,draft]{IEEEtran}
%\documentclass[12pt,draft]{IEEEtran}
%\documentclass[11pt,draft]{IEEEtran}
%\documentclass[11pt,final]{IEEEtran}
%\documentclass[11pt,ds,final]{my_IEEEtran}
\documentclass[11pt,onecolumn,draftcls]{IEEEtran}
%\documentclass[11pt]{IEEEtran}
%\documentclass[11pt]{IEEEtran}
%\documentclass[draft]{IEEEtran}
%\documentclass[9pt,twocolumn,technote,twoside]{IEEEtran}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

%\topmargin 0.125in

\usepackage{times}
\usepackage{subfigure}
%\usepackage{algorithmic}
\usepackage{algpseudocode}
\usepackage{algorithm}

%\usepackage{epsfig}
%\usepackage{graphics,graphicx,fancyhdr,amsfonts,amsmath,color,epic}
\usepackage[dvips]{graphics,graphicx}
%\usepackage{graphicx,graphics}
\DeclareGraphicsExtensions{.jpg,.pdf,.eps,.png}

\newtheorem {lemma}{Lemma}
\newtheorem {theorem}{Theorem}

\begin{document}

\title{An OpenCL Implementation of Wait-Free Sets}

\author{Sudarshan Shinde \\
        Bangalore, INDIA. \\
Email:sudarshan\_shinde@iitbombay.org}

\maketitle

%\markboth{IEEE Transactions On Automatic Control, Vol. XX, No. Y, Month 1999}
%{Murray and Balemi: Using the style file IEEEtran.sty}

%\noindent EDICS No :DSP-BANK, DSP-MULT, DSP-TFSR.

%\thispagestyle{plain}
%\pagestyle{plain}

\begin{abstract}

\end{abstract}

\begin{IEEEkeywords}
wait-free programming, multithreading, gpgpu, opencl.
\end{IEEEkeywords}

\footnotetext{Copyright (c) 2010 IEEE. Personal use of this material is permitted. However, permission to use this material for any other purposes must be obtained from the IEEE by sending a request to pubs-permissions@ieee.org.}

\pagebreak

\section{Implementation Details}

The algorithms described in the literarure do not describe memory management. In perticular, they do not take into consideration, what happens if a node is physically deleted, while another process it using that node.

OpenCL 2.0 defines Shared Virtual Memory (SVM), that could be used to share data between host and the GPU device, without explicit data transfer. However OpenCL does not support dynamic data allocation on GPU side, and requires that size of SVM be pre-defined. This restricts maximum size of a set.

Since an implementation needs to take care of memory management, in this implementation we allocate a node pool of size $N$ in SVM. Though this restricts set size to be less than $N$, it still highlights many implementation aspects of wait-free set implementation in heterogenous computing setting.

\section{Proof of Correctness}
{\fontsize{20}{20}
\begin{algorithm}
  \caption{Algorithm to delete marked nodes}
  \label{alg:deleteMarkedNode}
  \begin{algorithmic}[1]
    \Function{delMarkedNodes}{startRef, nextRef\&, nodePool}
      \State doneFlag = false;
      \While{(!doneFlag)}    
        \State [nextRef,startMark] := getPtr(startRef);
        \If{(!startMark)}
          \State [nextNextRef,nextMark] := getPtr(nextRef);
          \If{(nextMark)}
            \State casFlag = CAS(startRef:next,[nextRef,startMark],[nextNextRef,startMark]);
            \If{casFlag}
               \State PUT(nodePool,nextRef);
            \EndIf
          \Else
            \State
            \Return true;
          \EndIf
        \Else{}
          \State
          \Return false;  
        \EndIf
      \EndWhile        
    \EndFunction
  \end{algorithmic}
\end{algorithm}
}

\begin{theorem}
  If multiple threads are running algorithm \ref{alg:deleteMarkedNode}, then all of them will either return false, or return same unmarked nextRef.
\end{theorem}
\begin{proof}
  Consider the portion of the algorithm inside the while loop. It could be seen that the algorithm is trying to update the value of startRef:next. Each thread reads startRef:next at line 4, and atomically updates it at line 8. If multiple threads are updating it, only one thread will succeed, and so all the threads will have same value of startRef:next.

  Consider also that if some thread deletes startRef. This thread will also update startRef:next, making other threads running the algorithm return false.
\end{proof}

\begin{algorithm}
  \caption{Algorithm to find a key}
  \label{alg:find}
  \begin{algorithmic}[1]
    \Function{find}{key, nodePool}
       \State lid := getSIMDIndex();
       \State startRef := hashFunction(key);
       \State doneFlag := false;
       \While{(!doneFlag)}
          \State prevRef := startRef;
          \If{(lid = 1)}
             \State delStatus = delMarkedNode(prevRef,nextRef\&,nodePool);
          \EndIf
          \State waitAllSIMD();
          \State delStatus = broadcastSIMD(delStatus,1);
          \If{delStatus = true}
             \State maxVal = maxSIMD(nodePool,nextRef);
             \If{maxVal < key}
                \State prevRef = nextRef;
             \Else
                \State doneFlag = true;
                \If(anySIMD(val[lid] = key))
                   \Return true;
                \Else
                   \Return false;   
                \EndIf   
             \EndIf
          \Else
             \State prevRef = startRef;   
          \EndIf
       \EndWhile
    \EndFunction
  \end{algorithmic}
\end{algorithm}

%\Bibliographystyle{ieeetr}
%\include{references.bbl}

%%%%%\bibliography{bib-file}  % commented if *.bbl file included, as seen below

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%  End of IEEEsample.tex  %%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-06-05 Build/x64/Release/HTSBasics.hpp

@@ -1,39 +1,0 @@
-
-#ifndef _HTS_BASICS_HPP_
-#define _HTS_BASICS_HPP_
-
-#include <windows.h>
-#include <CL/opencl.h>
-#include "HTSConsts.hpp"
-
-class CRequest
-{
-public:
-  cl_uint   uiType;
-  cl_uint   uiKey;
-  cl_uint   uiFlags;
-  cl_uint   uiStatus;
-
-  CRequest()
-  {
-    uiKey    = uiFlags = 0;
-    uiStatus = 0;
-  };
-};
-
-class CFidS
-{
-public:
-  cl_uint          uiReqCount;
-  CRequest         pThreadRequest[THREAD_REQUEST_BUFFER_SIZE];
-
-  CFidS()
-  {
-    uiReqCount = 0;
-  };
-};
-
-typedef CFidS volatile*   TFid;
-typedef UINT              TEvent;
-
-#endif

### 2015-06-05 Build/x64/Release/HTSConsts.hpp

@@ -1,45 +1,0 @@
-#ifndef _HTS_CONSTS_HPP_
-#define _HTS_CONSTS_HPP_
-
-#define  HTS_OK                            (1)
-#define  HTS_NOT_OK                        (-1)
-
-#define  THREAD_REQUEST_BUFFER_SIZE        (512)
-
-#define  REQ_QUEUE_SIZE                    (1024)
-#define  REQ_QUEUE_SIZE_MASK               (0x03FF)
-
-#define  OCL_REQ_QUEUE_SIZE                (4096)
-#define  OCL_NODE_POOL_SIZE                (1048576)
-#define  OCL_HASH_TABLE_SIZE               (1024)
-#define  OCL_HASH_TABLE_MASK               (0x3FF)
-#define  OCL_WG_SIZE                       (256)
-#define  EMPTY_KEY                         (0) 
-  
-#define  SET_FLAG(f,b)                     ((f) | (b))
-#define  RESET_FLAG(f,b)                   ((f) & ~(b))
-#define  GET_FLAG(f,b)                     ((f)&(b))
-
-#define  GET_PTR(f)                        ((f)>> 1)
-#define  SET_PTR(f)                        ((f)<< 1)
-#define  GET_DBIT(f)                       ((f) & (uint)(0x01)) 
-#define  SET_DBIT(f)                       ((f) | (uint)(0x01)) 
-#define  RESET_DBIT(f)                     ((f) & (uint)(~0x01)) 
-
-enum eReqFlags
-  {
-    HTS_REQ_FULL      = 0x01,
-    HTS_REQ_QUEUED    = 0x02,
-    HTS_REQ_SUBMITTED = 0x04,
-    HTS_REQ_COMPLETED = 0x08,
-    HTS_REQ_ABORTED   = 0x10,
-    HTS_REQ_BLOCKING  = 0x20
-  };
-
-enum eReqType
-  {
-    HTS_REQ_TYPE_FIND   = 0x01,
-    HTS_REQ_TYPE_ADD    = 0x01,
-    HTS_REQ_TYPE_REMOVE = 0x01,
-  };
-#endif

### 2015-06-05 Build/x64/Release/HTSFrontEnd.hpp

@@ -1,60 +1,0 @@
-
-#pragma once
-
-#include <iostream>
-#include <windows.h>
-#include "HTSConsts.hpp"
-#include "HTSBasics.hpp"
-#include "HTSReqQueue.hpp"
-#include "HTSOcl.hpp"
-
-class CFrontEnd
-{
-public:
-  //constructor and destructor
-  CFrontEnd();
-  ~CFrontEnd();
-
-  UINT CFrontEnd::uiOpenFrontEnd();
-  UINT CFrontEnd::uiCloseFrontEnd();
-
-  //OCL functions
-  UINT          uiBindOCLContext(TOclContext* pOclContextIn);
-  UINT          uiBuildOCLKernels();
-  UINT          uiReleaseOCLKernels();
-
-  //interface functions
-  TFid          tRegister();
-  UINT          uiDeRegister(TFid tFid);
-  UINT          uiSubmitReq(TFid tFid, CRequest& cReq, TEvent& tEvent);
-  UINT          uiGetStatus(TFid tFid, TEvent& tEvent, cl_uint* ppStatus);
-
-  //query functions
-  UINT          uiGetThreadCount();
-
-  //top level thread function
-  DWORD         dwCFrontThread();
-
-private:
-  UINT             uiTidCount;
-  UINT             uiReqCount; 
-  CRequestQueue    tReqQueue;
-  HANDLE           tThreadHandle;
-  DWORD            dwThreadId;
-  HANDLE           tCloseThreadEvent; 
-  TOclContext*     pOclContext;
-
-  //svm buffer for shared request queue
-  TQueuedRequest*  pOclReqQueue; 
-  TLLNode*         pNodePool;
-  TLLNode*         pHashTable;
-  TMiscData*       pMiscData;
-  void*            pSVMBuf;
-
-  //ocl program and kernel
-  cl_program       oclProgram;
-  cl_kernel        oclKernel;
-  
-  //filename of the OCL code
-  const char*      pProgramFile = "HTSKernels.cl";
-};

### 2015-06-05 Build/x64/Release/HTSReqQueue.hpp

@@ -1,23 +1,0 @@
-
-#pragma once
-
-#include <windows.h>
-#include "HTSConsts.hpp"
-#include "HTSBasics.hpp"
-#include "HTSShared.hpp"
-
-class CRequestQueue
-{
-public:
-  CRequestQueue();
-  ~CRequestQueue();
-
-  LONG uiPut(TQueuedRequest* pReq);
-  LONG uiGet(TQueuedRequest* pReq);
-
-private:
-  TQueuedRequest  pReqQueue[REQ_QUEUE_SIZE];
-  LONG            uiReadIndex;
-  LONG            uiWriteIndex;
-};
-

### 2015-06-05 Build/x64/Release/HTSShared.hpp

@@ -1,59 +1,0 @@
-
-#ifndef _HTS_SHARED_HPP_
-#define _HTS_SHARED_HPP_
-
-#ifndef _OCL_CODE_
-
-#include <windows.h>
-#include "HTSBasics.hpp"
-
-typedef struct SQueuedRequest
-{
-  TFid            tFid;
-  cl_uint         uiReqId;
-  cl_uint         uiType; 
-  cl_uint         uiKey;
-  cl_uint         uiFlags;
-  cl_uint         uiStatus;
-} TQueuedRequest;
-
-typedef struct sLLNode
-{
-  cl_uint        pE[OCL_WG_SIZE];
-  cl_uint        uiNext; 
-} TLLNode;
-
-typedef struct sMiscData
-{
-  cl_uint       uiReadIndex;
-  cl_uint       uiWriteIndex;
-} TMiscData;
-
-#else
-#include "HTSConsts.hpp"
-
-typedef struct SQueuedRequest
-{
-  void*           pFid;
-  uint            uiReqId;
-  uint            uiType;
-  uint            uiKey;
-  uint            uiFlags;
-  uint            uiStatus;
-} TQueuedRequest;
-
-typedef struct sLLNode
-{
-  uint           pE[OCL_WG_SIZE];
-  uint           uiNext; 
-} TLLNode;
-
-typedef struct sMiscData
-{
-  uint       uiReadIndex;
-  uint       uiWriteIndex;
-} TMiscData;
-
-#endif
-
-#endif

### 2015-06-05 Code/Inc/HTSConsts.hpp

@@ -22,9 +22,10 @@
 
 #define  GET_PTR(f)                        ((f)>> 1)
 #define  SET_PTR(f)                        ((f)<< 1)
-#define  GET_DBIT(f)                       ((f) & (uint)(0x01)) 
-#define  SET_DBIT(f)                       ((f) | (uint)(0x01)) 
-#define  RESET_DBIT(f)                     ((f) & (uint)(~0x01)) 
+#define  GET_DBIT(f)                       ((f) & (0x01)) 
+#define  SET_DBIT(f)                       ((f) | (0x01)) 
+#define  RESET_DBIT(f)                     ((f) & (~0x01)) 
+#define  SET_MPTR(f,b)                     (((f)<< 1) | (b))
 
 enum eReqFlags
   {

### 2015-06-05 Code/Src/HTSFrontEnd.cpp

@@ -99,17 +99,22 @@ UINT CFrontEnd::uiBuildOCLKernels()
     {
       pNodePool[i].uiNext = 0;
     }
-  
-  for(UINT i = 0; i < OCL_NODE_POOL_SIZE; ++i)
+
+  pMiscData->uiReadIndex  = OCL_HASH_TABLE_SIZE;
+  pMiscData->uiWriteIndex = OCL_HASH_TABLE_SIZE + 1;
+
+  cl_uint uiStartIndex = OCL_HASH_TABLE_SIZE + 2;
+  cl_uint uiEndIndex   = OCL_HASH_TABLE_SIZE + OCL_NODE_POOL_SIZE -1;  
+
+  for(cl_uint i = uiStartIndex; i < uiEndIndex; ++i)
     {
-      UINT j = i + OCL_HASH_TABLE_SIZE;
-      
-      pNodePool[j].uiNext = j + 1;
+      cl_uint j = SET_MPTR((i+1),1);
+      pNodePool[i].uiNext = j;
     }
   
-  pNodePool[OCL_NODE_POOL_SIZE + OCL_HASH_TABLE_SIZE -1].uiNext = 0;
-  pMiscData->uiReadIndex  = OCL_HASH_TABLE_SIZE;
-  pMiscData->uiWriteIndex = OCL_HASH_TABLE_SIZE + OCL_NODE_POOL_SIZE -1;
+  pNodePool[uiEndIndex].uiNext              = 0;
+  pNodePool[pMiscData->uiReadIndex].uiNext  = SET_MPTR(uiStartIndex,1);
+  pNodePool[pMiscData->uiWriteIndex].uiNext = SET_MPTR(uiEndIndex,1);  
 
   //create the program
   std::string sourceStr;

### 2015-06-12 Docs/paper.tex
doc updated

--- 2015-06-05 Code/Docs/paper.tex
@@
 %\documentclass[11pt,ds,final]{my_IEEEtran}
-\documentclass[11pt,onecolumn,draftcls]{IEEEtran}
+%\documentclass[11pt,onecolumn,draftcls]{IEEEtran}
 %\documentclass[11pt]{IEEEtran}
-%\documentclass[11pt]{IEEEtran}
+\documentclass[11pt,onecolumn]{IEEEtran}
 %\documentclass[draft]{IEEEtran}
@@
 \section{Proof of Correctness}
-{\fontsize{20}{20}
 \begin{algorithm}
-  \caption{Algorithm to delete marked nodes}
+  \caption{Delete all marked nodes}
   \label{alg:deleteMarkedNode}
-  \begin{algorithmic}[1]
-    \Function{delMarkedNodes}{startRef, nextRef\&, nodePool}
+  \begin{algorithmic}[5]
+    \Function{delMarkedNodes}{startRef, nodePool}
       \State doneFlag = false;
@@
             \If{casFlag}
-               \State PUT(nodePool,nextRef);
+               \State freeNode(nodePool,nextRef);
             \EndIf
@@
 \end{algorithm}
-}
 
@@
 \begin{algorithm}
-  \caption{Algorithm to find a key}
+  \caption{Check next node for key}
+  \label{alg:check}
+  \begin{algorithmic}[5]
+    \Function{checkKey}{key, prevRef\&, nodePool}
+       \State [nextRef,prevMark] := getPtr(prevRef);
+       \If {(prevMark)}
+         \State
+         \Return {\small NODE\_DELETED}.
+       \EndIf
+       \If {(nextRef = 0)}
+         \State
+         \Return {\small KEY\_NOT\_DELETED}.
+       \EndIf
+
+       \State [nnRef,nextMark] := getPtr(nextRef);
+       \If {(nextMark)}
+         \State
+         \Return {\small NODE\_NEXT}.
+       \EndIf
+
+       \State maxVal := simdMax(nodePool,nextRef);
+         \If{maxVal $<$ key}
+            \State prevRef := nextRef;
+            \Return {\small NODE\_NEXT}.
+         \Else
+           \If{simdAny(val[lid] = key)}
+               \State
+               \Return {\small KEY\_FOUND};
+           \Else
+               \State               
+               \Return {\small KEY\_NOT\_FOUND};   
+           \EndIf   
+         \EndIf
+    \EndFunction
+  \end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+  \caption{Find a key in the set}
   \label{alg:find}
-  \begin{algorithmic}[1]
-    \Function{find}{key, nodePool}
-       \State lid := getSIMDIndex();
+  \begin{algorithmic}[5]
+    \Function{find}{key, prevRef\&, nodePool}
+       \State lid := simdGetIndex();
        \State startRef := hashFunction(key);
+       \State prevRef  := startRef;
        \State doneFlag := false;
        \While{(!doneFlag)}
+          \If{(lid = 1)}
+             \State delStatus := delMarkedNode(prevRef,nodePool);
+          \EndIf
+          \State simdBarrier();
+          \State delStatus = simdBroadcast(delStatus,1);
+          \If{delStatus = true}
+             \State keyStatus := checkKey(key, prevRef, nodePool);
+             \If{(keyStatus = NODE\_DELETED)}
                 \State prevRef := startRef;
-          \If{(lid = 1)}
-             \State delStatus = delMarkedNode(prevRef,nextRef\&,nodePool);
+             \ElsIf{(keyStatus = KEY\_FOUND)}
+                \State 
+                \Return true
+             \ElsIf{(keyStatus = KEY\_NOT\_FOUND)}
+                \State 
+                \Return false
              \EndIf
-          \State waitAllSIMD();
-          \State delStatus = broadcastSIMD(delStatus,1);
-          \If{delStatus = true}
-             \State maxVal = maxSIMD(nodePool,nextRef);
-             \If{maxVal < key}
-                \State prevRef = nextRef;
           \Else
-                \State doneFlag = true;
-                \If(anySIMD(val[lid] = key))
-                   \Return true;
-                \Else
+             \State prevRef := startRef;   
+          \EndIf
+       \EndWhile
+    \EndFunction
+  \end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+  \caption{Insert a key in the set}
+  \label{alg:insert}
+  \begin{algorithmic}[5]  
+    \Function{insert}{key, nodePool}
+      \State doneFlag := false;
+      \While{(!doneFlag)}
+        \State findStatus := find(key, prevRef\&, nextRef\&, nodePool);
+        \If{(findStaus = true)}
+          \State
           \Return false;
         \EndIf
+        \State minIndex := getMinEmptySlot(nextRef,nodePool);
+        \If{minIndex = 0} \Comment No empty slot.
+          \State insertStatus := insertNodeAndKey(key, prevRef\&,nextRef\&,nodePool);
+        \Else
+          \State insertStatus := insertKey(key, minIndex, nextRef\&,nodePool);
         \EndIf
-          \Else
-             \State prevRef = startRef;   
+        \If{insertStatus = true}
+          \State
+          \Return true;
         \EndIf
       \EndWhile
+    \EndFunction
+  \end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+  \caption{Find empty slot with minimum index}
+  \label{alg:minindex}
+  \begin{algorithmic}[5]  
+    \Function{getMinEmptySlot}{nextRef, nodePool}
+      \State val := nodePool[nextRef]:V[lid];
+      \State indicator := (val = EMPTY\_SLOT)?lid:0;
+      \If {(simdALL(indicator = 0))}
+        \State minIndex := 0;
+      \Else
+        \State minIndex := simdMin(indicator);
+      \EndIf
+      \Return minIndex;        
+    \EndFunction
+  \end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+  \caption{Insert a node and a key}
+  \label{alg:insnodekey}
+  \begin{algorithmic}[5]  
+    \Function{insertNodeAndKey}{key, prevRef\&, nextRef\&, nodePool}
+      \State newNRef := Alloc(nodePool);
+      \State newNNRef := Alloc(nodePool);
+      \State newNRef:next := [newNNRef,0];
+      \If{(nodePool[nextRef]:V[lid] < key)}
+        \State nodePool[newNRef]:V[lid] := nodePool[nextRef]:V[lid];
+        \State nodePool[newNNRef]:V[lid] := EMPTY\_SLOT;
+      \Else
+        \State nodePool[newNNRef]:V[lid] := nodePool[nextRef]:V[lid];
+        \State nodePool[newNPRef]:V[lid] := EMPTY\_SLOT;
+      \EndIf
+      \State minIndex := getMinEmptySlot(newNRef,nodePool);
+      \State nodePool[newNRef]:V[minIndex] := key;
+      \State nodePool[newNNPtr]:next := [nextRef,0];
+      \State status := CAS(nodePool[prevRef]:next,[nextRef,0],newNPtr);
+      \Return status;
+    \EndFunction
+  \end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+  \caption{Insert a key in a node}
+  \label{alg:inskey}
+  \begin{algorithmic}[5]  
+    \Function{insertKey}{key, minIndex, nextRef\&, nodePool}
+      \If{lid = 1}
+        \State status := CAS(nodePool[nextRef]:V[minIndex],EMPTY\_SLOT,key);
+      \EndIf
+      \State simdWait();
+      \State status = simdBroadcast(status, 1);
+      \Return status;
+    \EndFunction
+  \end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+  \caption{Delete a key from the set}
+  \label{alg:delkey}
+  \begin{algorithmic}[5]  
+    \Function{remove}{key, nodePool}
+      \State doneFlag := false;
+      \While{(!doneFlag)}
+        \State findStatus := find(key, prevRef\&, nextRef\&, nodePool);
+        \If{(findStaus = false)}
+          \State
+          \Return false;
+        \EndIf
+        \State val   := nodePool[nextRef]:V[lid];
+        \If{(val = key)}
+          \State status := CAS(nodePool[nextRef]:V[lid],key,EMPTY\_SLOT);
+        \EndIf
+        \State simdWait();
+        \State status := simdBrodacast(status);
+        \If{(status = true)}
+          \State status := deleteNode(prevRef\&, nextRef\&, nodePool);
+          \Return status;
+        \Else
+          \State
+          \Return false;
+        \EndIf
+      \EndWhile
+    \EndFunction
+  \end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+  \caption{Delete a node}
+  \label{alg:delnode}
+  \begin{algorithmic}[5]  
+    \Function{deleteNode}{prevRef\&, nextRef\&, nodePool}
+         \State val := nodePool[nextRef]:V[lid];
+         \State status := simdAll(val,EMPTY\_SLOT);
+         \If{(status = true)}
+           \State [nnRef,nextMark] := getPtr(nextRef);
+           \State newMark := 1;
+           \If{(lid = 1)}
+              \State status := CAS(nodePool[nextRef]:next,[nnRef,nextMark],[nnRef,newMark]);
+              \If{(status = true)}
+                \State status = delMarkedNodes(prevRef,NodePool); 
+              \EndIf
+           \EndIf
+           \State simdWait();
+           \State status = simdBroadcast(status,1);
+           \State
+           \Return status;
+         \EndIf
     \EndFunction

### 2015-06-15 Docs/paper.tex
doc chg

@@
 \usepackage{algorithm}
+%\renewcommand{\algorithmicrequire}{\textbf{Input:}}
+%\renewcommand{\algorithmicensure}{\textbf{Output:}}
 
@@
 \begin{algorithm}
-  \caption{Delete all marked nodes}
+  \caption{Deletes all marked nodes beyond {\it startRef}}
   \label{alg:deleteMarkedNode}
-  \begin{algorithmic}[5]
-    \Function{delMarkedNodes}{startRef, nodePool}
+
+  \begin{algorithmic}[1]
+    \Require
+       \Statex startRef:Reference to the node beyond which all
+               marked nodes are to be deleted. 
+    \Ensure
+       \Statex All marked nodes beyond {\it startRef} are deleted.
+       \Statex {\it nextRef} returns next unmarked node beyond {\it startRef}.  
+       \Statex Returns {\it true} if all marked nodes are deleted,
+               {\it false} if node referenced by {\it startRef} gets deleted.
+
+    \Statex   
+    \Function{delMarkedNodes}{startRef, nextRef\&}
       \State doneFlag = false;
       \While{(!doneFlag)}    
-        \State [nextRef,startMark] := getPtr(startRef);
+        \State [nextRef,startMark] := getUnmarkedRef(startRef);
         \If{(!startMark)}
-          \State [nextNextRef,nextMark] := getPtr(nextRef);
+          \State [nextNextRef,nextMark] := getUnmarkedRef(nextRef);
           \If{(nextMark)}
-            \State casFlag = CAS(startRef:next,[nextRef,startMark],[nextNextRef,startMark]);
-            \If{casFlag}
-               \State freeNode(nodePool,nextRef);
+            \State status = CAS(nodePool[startRef]:next,[nextRef,startMark],[nextNextRef,startMark]);
+            \If{(status = true)}
+               \State freeNode(nextRef);
             \EndIf
@@
 \begin{theorem}
-  If multiple threads are running algorithm \ref{alg:deleteMarkedNode}, then all of them will either return false, or return same unmarked nextRef.
+  A process running algorithm \ref{alg:deleteMarkedNode}, then it will either return next unmarked node after {\it startRef} in {\it nextRef}, or return {\it false}.
 \end{theorem}
-\begin{proof}
-  Consider the portion of the algorithm inside the while loop.
-It could be seen that the algorithm is trying to update the value of startRef:next.
-Each thread reads startRef:next at line 4, and atomically updates it at line 8.
-If multiple threads are updating it, only one thread will succeed, and so all the threads will have same value of startRef:next.
-
-  Consider also that if some thread deletes startRef. This thread will also update startRef:next, making other threads running the algorithm return false.
-\end{proof}
+\begin{IEEEproof}
+  The proof consists of the following parts.
+  \begin{enumerate}
+    \item The state of the linked list copied to internal variables {\it nextRef} and {\it nnRef} is valid as they are read simultaneously with {\it startMark} and {\it nextMark} respectively, and both these flags are checked.
+    \item If this state remains valid, then CAS operation is successful.
+    \item If this state is changed by any other process, this change is completely reflected in {\it startRef:next}.  
+\end{enumerate} 
+\end{IEEEproof}
 

### 2015-06-19 Docs/paper.tex
doc changed

@@
 \begin{algorithm}
-  \caption{Deletes all marked nodes beyond {\it startRef}}
+  \caption{Deletes all marked nodes that follow a given node}
   \label{alg:deleteMarkedNode}
@@
     \Require
-       \Statex startRef:Reference to the node beyond which all
-               marked nodes are to be deleted. 
+        \Statex startRef:Reference to the starting node. Marked nodes
+                that follow this are to be deleted. 
     \Ensure
-       \Statex All marked nodes beyond {\it startRef} are deleted.
-       \Statex {\it nextRef} returns next unmarked node beyond {\it startRef}.  
+       \Statex All marked nodes following {\it startRef} are deleted.
        \Statex Returns {\it true} if all marked nodes are deleted,
@@
     \Statex   
-    \Function{delMarkedNodes}{startRef, nextRef\&}
+    \Function{delMarkedNodes}{startRef}
       \State doneFlag = false;
@@
           \If{(nextMark)}
-            \State status = CAS(nodePool[startRef]:next,[nextRef,startMark],[nextNextRef,startMark]);
+            \State status = CAS(startRef:next,[nextRef,startMark],[nextNextRef,startMark]);
             \If{(status = true)}
@@
   \label{alg:check}
-  \begin{algorithmic}[5]
-    \Function{checkKey}{key, prevRef\&, nodePool}
-       \State [nextRef,prevMark] := getPtr(prevRef);
+  \begin{algorithmic}[1]
+    \Require
+       \Statex {\it key} to be checked.
+       \Statex {\it prevRef}, reference to node next to which the key is to
+               be checked.
+    \Ensure
+       \Statex Nodes referenced by {\it prevRef} and {\it prevRef:next} are
+               unmarked. If they are marked, returns NODE\_DELETED and
+               NODE\_NEXT respectively.
+       \Statex If all values in {\it prevRef:next} $<$ {\it key}, moves
+               {\it prevRef} to {\it prevRef:next}.          
+       \Statex If values in {\it prevRef:next} $<$ {\it key}, checks for the key.
+               Returns KEY\_FOUND or KEY\_NOT\_FOUND respectively.
+
+    \Statex   
+    \Function{checkKey}{key, prevRef\&}
+       \State [nextRef,prevMark] := getUnmarkedPtr(prevRef);
        \If {(prevMark)}
@@
          \State
-         \Return {\small KEY\_NOT\_DELETED}.
+         \Return {\small KEY\_NOT\_FOUND}.
        \EndIf
 
-       \State [nnRef,nextMark] := getPtr(nextRef);
+       \State [nnRef,nextMark] := getUnmarkedPtr(nextRef);
        \If {(nextMark)}
@@
 
-       \State maxVal := simdMax(nodePool,nextRef);
+       \State maxVal := simdMAX(nextRef:V[lid]);
        \If{maxVal $<$ key}
@@
        \Else
-           \If{simdAny(val[lid] = key)}
+           \If{simdANY(nextRef:V[lid] = key)}
                \State
@@
   \label{alg:find}
-  \begin{algorithmic}[5]
-    \Function{find}{key, prevRef\&, nodePool}
-       \State lid := simdGetIndex();
+  \begin{algorithmic}[1]
+    \Require
+       \Statex {\it key} to be searched.
+    \Ensure
+       \Statex {\it prevRef}, such that next node either has key or key could
+               be inserted to it.
+       \Statex Returns {\it true} if key is found else returns {\it false}.
+
+    \Function{find}{key, prevRef\&}
+       \State lid := simdINDEX();
        \State startRef := hashFunction(key);
@@
           \If{(lid = 1)}
-             \State delStatus := delMarkedNode(prevRef,nodePool);
+             \State delStatus := delMarkedNode(prevRef);
           \EndIf
-          \State simdBarrier();
-          \State delStatus = simdBroadcast(delStatus,1);
+          \State simdBARRIER();
+          \State delStatus = simdBROADCAST(delStatus,1);
           \If{delStatus = true}
-             \State keyStatus := checkKey(key, prevRef, nodePool);
+             \State keyStatus := checkKey(key, prevRef);
              \If{(keyStatus = NODE\_DELETED)}
@@
   \label{alg:insert}
-  \begin{algorithmic}[5]  
-    \Function{insert}{key, nodePool}
+  \begin{algorithmic}[1]
+    \Require
+       \Statex {\it key} to be searched.
+    \Ensure
+       \Statex Returns {\it false} if key is found else inserts the {\it key}.
+
+    \Statex
+    \Function{insert}{key}
       \State doneFlag := false;
       \While{(!doneFlag)}
-        \State findStatus := find(key, prevRef\&, nextRef\&, nodePool);
+        \State findStatus := find(key, prevRef);
         \If{(findStaus = true)}
@@
         \EndIf
+        \State [nextRef, prevMark] = getUnmarkedRef(prevRef);
+        \If{(prevMark = 0)}
+          \State insertStatus = false;
           \State minIndex := getMinEmptySlot(nextRef,nodePool);
-        \If{minIndex = 0} \Comment No empty slot.
-          \State insertStatus := insertNodeAndKey(key, prevRef\&,nextRef\&,nodePool);
-        \Else
-          \State insertStatus := insertKey(key, minIndex, nextRef\&,nodePool);
+          \If{(minIndex = 0)} \Comment No empty slot.
+            \State insertStatus := insertNodeAndKey(key, prevRef,nextRef);
+          \ElsIf{(minIndex > 0)}
+            \State insertStatus := insertKey(key, minIndex, prevRef, nextRef);
           \EndIf
@@
             \Return true;
+          \EndIf
         \EndIf
@@
   \label{alg:minindex}
-  \begin{algorithmic}[5]  
-    \Function{getMinEmptySlot}{nextRef, nodePool}
-      \State val := nodePool[nextRef]:V[lid];
+  \begin{algorithmic}[1]
+    \Require
+      \Statex {\it nextRef} in which minumum index to empty slot is to be
+              found.
+    \Ensure
+      \Statex Returns {\it -1} if {\it nextRef} is deleted, {\it 0} if no
+              empty slot is found, or minimum index to empty slot.
+
+    \Function{getMinEmptySlot}{nextRef}
+      \State val := nextRef:V[lid];
       \State indicator := (val = EMPTY\_SLOT)?lid:0;
@@
       \Else
-        \State minIndex := simdMin(indicator);
+        \State minIndex := simdMIN(indicator);
       \EndIf
+      \State [nnRef,nextMark] := getUnmarkedPtr(nextRef);
+      \If{(nextMark = 0)}
+        \State
         \Return minIndex;
+      \Else
+        \State
+        \Return -1;
+      \EndIf  
     \EndFunction
@@
   \label{alg:insnodekey}
-  \begin{algorithmic}[5]  
-    \Function{insertNodeAndKey}{key, prevRef\&, nextRef\&, nodePool}
-      \State newNRef := Alloc(nodePool);
-      \State newNNRef := Alloc(nodePool);
+  \begin{algorithmic}[1]
+    \Require
+      \Statex {\it key} to be inserted.
+      \Statex {\it prefRef} and {\it nextRef} give window in which new node
+              and key are to be inserted.
+    \Ensure
+       \Statex Returns {\it true} if successful.
+
+    \Function{insertNodeAndKey}{key, prevRef, nextRef}
+      \If{(lid = 1)} 
+        \State newNRef := newNode();
+        \State newNNRef := newNode();
+      \EndIf
+      \State simdBARRIER();
+      \State newNRef  := simdBROADCAST(newNRef,1);
+      \State newNNRef := simdBROADCAST(newNRef,1);
+
       \State newNRef:next := [newNNRef,0];

### 2015-07-02 Docs/paper.tex
doc changed

@@
 Though this restricts set size to be less than $N$, it still highlights many implementation aspects of wait-free set implementation in heterogenous computing setting.
+
+\section{The Algorithm}
+The algorithm consists of a modification of the wait-free linked list to support replacing a node.
+
+A {\it packed} reference consists of an unmarked reference, a {\it mark} bit to indicate if the node is marked and an {\it retain} bit to indicate that unmarked reference could not be changed.
+It also has a {\it free} bit to indicate that whether the node is occupied or free.
+These three bits are arranged as $Bits = [fBit,rBit,mBit]$.
+
+We also have the following methods
+
+\begin{enumerate}
+    \item $[ref, bits] = unpackRef(pref)$.
+\end{enumerate}
+
+\begin{algorithm}
+  \caption{snips next node if it is marked and could be snipped}
+  \label{alg:snip}
+
+  \begin{algorithmic}[1]
+    \Require
+        \Statex startRef:Reference to the starting node.
+    \Ensure
+       \Statex next node will be snipped.
+    \Statex   
+    \Function{snip}{startRef}
+      \State pPRef = startRef:next;
+      \State [nRef,pBits] = unpackRef(startRef:next);
+      \If{(pBits = [0,0,0])}
+        \State [nnRef,nBits] = unpackRef(pRef:next):
+        \If{(nBits = [0,x,1])}
+          \State status = CAS(startRef:next,pPRef,[nnRef,pBits]);
+          \State
+          \Return status;
+        \Else
+          \State
+          \Return false;
+        \EndIf
+      \Else
+        \State
+        \Return false;
+      \EndIf
+    \EndFunction
+  \end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+  \caption{Replaces next node with a new node}
+  \label{alg:replace}
+
+  \begin{algorithmic}[1]
+    \Require
+        \Statex startRef:Reference to the starting node.
+    \Ensure
+       \Statex next node will be replaced by new node.
+    \Statex   
+    \Function{replace}{startRef, newRef}
+      \State pPRef = startRef:next;    
+      \State [nRef,pBits] = unpackRef(startRef:next);
+      \If{([pBits] = [0,0,0])}
+        \State nPRef = nRef:next;    
+        \State [nnRef,nBits] = unpackRef(nRef:next);
+        \If{(nBits = [0,x,0])}
+          \State status = CAS(nRef:next,nPRef,[nnRef,[0,1,0]]);
+          \If{(status = false)}
+            \State
+            \Return false;
+          \EndIf  
+        \Else
+          \State
+          \Return false;
+        \EndIf
+        \State newRef:next = [nnRef,[0,0,0]];
+        \State status = CAS(startRef:next,pPRef,[newRef,pBits]);
+        \If{(status = false)}
+          \State
+          \Return false;
+        \EndIf
+      \Else
+        \State
+        \Return false;
+      \EndIf
+      \State
+      \Return true;
+    \EndFunction
+  \end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+  \caption{cleans all the nodes that are logically deleted and could be physically deleted}
+  \label{alg:clean}
+  \begin{algorithmic}[1]
+    \Require
+        \Statex startRef:Reference to the starting node.
+    \Ensure
+       \Statex cleans all the logically deleted nodes.
+    \Statex   
+    \Function{clean}{startRef, nextRef\&}
+      \State pRef  = startRef;
+      \While{(done = 0)}
+        \State nPRef = pRef:next;
+        \State [nRef,prBit,pmBit] = unpackRef(nPRef);
+        \If({prBit = 0})
+          \State status = snip(pRef);
+        \Else
+          \State   
+        \EndIf
+      \EndWhile
+    \EndFunction
+  \end{algorithmic}
+\end{algorithm}
 

### 2015-07-03 Docs/paper.tex
doc changed

@@
 \begin{algorithm}
-  \caption{snips next node if it is marked and could be snipped}
+  \caption{Snips next node if it is marked and could be snipped}
   \label{alg:snip}
@@
   \begin{algorithmic}[1]
-    \Require
-        \Statex startRef:Reference to the starting node.
-    \Ensure
-       \Statex next node will be snipped.
-    \Statex   
+    %\Require
+    %    \Statex startRef:Reference to the starting node.
+    %\Ensure
+    %   \Statex  next node will be snipped.
+    %\Statex   
     \Function{snip}{startRef}
@@
       \State [nRef,pBits] = unpackRef(startRef:next);
-      \If{(pBits = [0,0,0])}
-        \State [nnRef,nBits] = unpackRef(pRef:next):
+      \If{(pBits = [0,0,x])}
+        \State [nnRef,nBits] = unpackRef(nRef:next):
         \If{(nBits = [0,x,1])}
           \State status = CAS(startRef:next,pPRef,[nnRef,pBits]);
+          \If{(status = true)}
+             \State FREE(nRef);
              \State 
-          \Return status;
+             \Return {\it snipped};
           \Else
              \State
-          \Return false;
+             \Return {\it failed};
           \EndIf
@@
           \State
-        \Return false;
+          \Return {\it next\_unmarked};
+        \EndIf
+      \Else
+        \State
+        \Return {\it start\_invalid};
       \EndIf
@@
   \begin{algorithmic}[1]
-    \Require
-        \Statex startRef:Reference to the starting node.
-    \Ensure
-       \Statex next node will be replaced by new node.
+    %\Require
+    %    \Statex startRef:Reference to the starting node.
+    %\Ensure
+    %   \Statex next node will be replaced by new node.
     \Statex   
@@
             \State
-            \Return false;
+            \Return {\it retain\_failed};
           \EndIf  
@@
           \State
-          \Return false;
+          \Return {\it invalid\_nbits};
         \EndIf
@@
         \State status = CAS(startRef:next,pPRef,[newRef,pBits]);
-        \If{(status = false)}
+        \If{(status = true)}
+          \State FREE(nRef);
           \State
-          \Return false;
+          \Return {\it replaced}; 
+        \Else
+          \State
+          \Return {\it failed};
         \EndIf
@@
         \State
-        \Return false;
+        \Return {\it invalid\_pbits};
       \EndIf
-      \State
-      \Return true;
     \EndFunction
@@
   \begin{algorithmic}[1]
+    %\Require
+    %    \Statex startRef:Reference to the starting node.
+    %\Ensure
+    %   \Statex cleans all the logically deleted nodes.
+    \Statex   
+    \Function{clean}{startRef, nextRef\&}
+      \State pRef  = startRef;
+      \State nextRef  = {\it null};
+      \While{(true)}
+        \State status = snip(pRef);
+        \State [nRef,pBits] = unpackRef(pRef:next);
+        \If{(status = {\it next\_unmarked})}
+          \State nextRef = nRef;
+          \State
+          \Return status;
+        \ElsIf{status = {\it start\_invalid}}
+          \If{(pBits = [0,1,x])}
+            \State pRef = nRef; 
+          \Else
+            \If{(pRef = startRef)}
+              \State
+              \Return {\it start\_invalid}
+            \Else
+              \State pRef = startRef;  
+            \EndIf
+          \EndIf
+        \EndIf
+      \EndWhile
+    \EndFunction
+  \end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+  \caption{checks for valid window.}
+  \label{alg:window}
+  \begin{algorithmic}[1]
+    %\Require
+    %    \Statex startRef:Reference to the starting node.
+    %\Ensure
+    %   \Statex cleans all the logically deleted nodes.
+    \Statex   
+    \Function{window}{key, prevRef, nextRef, index\&}
+      \State status = false;
+      \If{(prevRef != {\it Null})}
+        \State [nRef, pBits] = unpackRef(prevRef:next);
+        \If{(pBits != [0,x,0])}
+          \State 
+          \Return {\it invalid\_prev\_bits}; ; 
+        \EndIf
+        \If{(nRef != nextRef)}
+          \State 
+          \Return {\it invalid\_next\_ref}; 
+        \EndIf
+        \State pMaxVal = simdMAX(prevRef:val);  
+        \If{(key $<=$ pMaxVal)}
+          \State 
+          \Return {\it window\_not\_found};; 
+        \EndIf
+      \EndIf
+      \State [nnRef, nBits] = unpackRef(nextRef:next);
+      \If{(nBits != [0,x,0])}
+        \State 
+        \Return {\it invalid\_next\_bits}; 
+      \EndIf
+      \State pMaxVal = simdMAX(nextRef:val);  
+      \If{(key $<=$ pMaxVal)}
+        \State 
+        \Return {\it window\_not\_found};
+      \Else
+        \If{(simdANY((key = nextRef:Val), index))}
+          \State
+          \Return {\it key\_found}
+        \Else
+          \State
+          \Return {\it window\_found}
+        \EndIf
+      \EndIf
+    \EndFunction
+  \end{algorithmic}
+\end{algorithm}
+
+\begin{algorithm}
+  \caption{finds a key and returns a window to it.}
+  \label{alg:find}
+  \begin{algorithmic}[1]
     \Require
@@
     \Statex   
-    \Function{clean}{startRef, nextRef\&}
-      \State pRef  = startRef;
-      \While{(done = 0)}
-        \State nPRef = pRef:next;
-        \State [nRef,prBit,pmBit] = unpackRef(nPRef);
-        \If({prBit = 0})
-          \State status = snip(pRef);
-        \Else
+    \Function{find}{key, prevRef\&, nextRef\&, index\&}
+      \State startRef = hash(key);
+      \State prevRef = nextRef = {\it Null};
+      \State index = 0;      
+      \While(true)
+        \State pRef = {\it Null};
+        \State nRef = startRef;
+        \State status = {\it window\_not\_found};
+        \While{(status = {\it window\_not\_found})}
+          \State status = WINDOW(key, pRef, nRef, index);
+          \If{(status = {\it window\_not\_found})}
+            \State pRef = nRef;
+            \State status2 = CLEAN(pRef,nRef);
+            \If{(status2 = {\it start\_invalid})}
+              \State status = {\it window\_not\_found}
+            \EndIf
+          \EndIf
+        \EndWhile
+        \If{(status = {\it window\_found})}
           \State
+          \Return status;
+        \EndIf
+        \If{(status = {\it key\_found})}
+          \State
+          \Return status;
         \EndIf
@@
 \section{Proof of Correctness}
-\begin{algorithm}
-  \caption{Deletes all marked nodes that follow a given node}
-  \label{alg:deleteMarkedNode}
-
-  \begin{algorithmic}[1]
-    \Require
-        \Statex startRef:Reference to the starting node. Marked nodes
-                that follow this are to be deleted. 
-    \Ensure
-       \Statex All marked nodes following {\it startRef} are deleted.
-       \Statex Returns {\it true} if all marked nodes are deleted,
-               {\it false} if node referenced by {\it startRef} gets deleted.
-
-    \Statex   
-    \Function{delMarkedNodes}{startRef}
-      \State doneFlag = false;
-      \While{(!doneFlag)}    
-        \State [nextRef,startMark] := getUnmarkedRef(startRef);
-        \If{(!startMark)}
-          \State [nextNextRef,nextMark] := getUnmarkedRef(nextRef);
-          \If{(nextMark)}
-            \State status = CAS(startRef:next,[nextRef,startMark],[nextNextRef,startMark]);
-            \If{(status = true)}
-               \State freeNode(nextRef);
-            \EndIf
-          \Else
-            \State
-            \Return true;
-          \EndIf
-        \Else{}
-          \State
-          \Return false;  
-        \EndIf
-      \EndWhile        
-    \EndFunction
-  \end{algorithmic}
-\end{algorithm}
-
-\begin{theorem}
-  A process running algorithm \ref{alg:deleteMarkedNode}, then it will either return next unmarked node after {\it startRef} in {\it nextRef}, or return {\it false}.
-\end{theorem}
-\begin{IEEEproof}
-  The proof consists of the following parts.
-  \begin{enumerate}
-    \item The state of the linked list copied to internal variables {\it nextRef} and {\it nnRef} is valid as they are read simultaneously with {\it startMark} and {\it nextMark} respectively, and both these flags are checked.
-    \item If this state remains valid, then CAS operation is successful.
-    \item If this state is changed by any other process, this change is completely reflected in {\it startRef:next}.  
-\end{enumerate} 
-\end{IEEEproof}
-
-\begin{algorithm}
-  \caption{Check next node for key}
-  \label{alg:check}
-  \begin{algorithmic}[1]
-    \Require
-       \Statex {\it key} to be checked.
-       \Statex {\it prevRef}, reference to node next to which the key is to
-               be checked.
-    \Ensure
-       \Statex Nodes referenced by {\it prevRef} and {\it prevRef:next} are
-               unmarked. If they are marked, returns NODE\_DELETED and
-               NODE\_NEXT respectively.
-       \Statex If all values in {\it prevRef:next} $<$ {\it key}, moves
-               {\it prevRef} to {\it prevRef:next}.          
-       \Statex If values in {\it prevRef:next} $<$ {\it key}, checks for the key.
-               Returns KEY\_FOUND or KEY\_NOT\_FOUND respectively.
-
-    \Statex   
-    \Function{checkKey}{key, prevRef\&}
-       \State [nextRef,prevMark] := getUnmarkedPtr(prevRef);
-       \If {(prevMark)}
-         \State
-         \Return {\small NODE\_DELETED}.
-       \EndIf
-       \If {(nextRef = 0)}
-         \State
-         \Return {\small KEY\_NOT\_FOUND}.
-       \EndIf
-
-       \State [nnRef,nextMark] := getUnmarkedPtr(nextRef);
-       \If {(nextMark)}
-         \State
-         \Return {\small NODE\_NEXT}.
-       \EndIf
-
-       \State maxVal := simdMAX(nextRef:V[lid]);
-       \If{maxVal $<$ key}
-           \State prevRef := nextRef;
-           \Return {\small NODE\_NEXT}.
-       \Else
-           \If{simdANY(nextRef:V[lid] = key)}
-               \State
-               \Return {\small KEY\_FOUND};
-           \Else
-               \State               
-               \Return {\small KEY\_NOT\_FOUND};   
-           \EndIf   
-         \EndIf
-    \EndFunction
-  \end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}
-  \caption{Find a key in the set}
-  \label{alg:find}
-  \begin{algorithmic}[1]
-    \Require
-       \Statex {\it key} to be searched.
-    \Ensure
-       \Statex {\it prevRef}, such that next node either has key or key could
-               be inserted to it.
-       \Statex Returns {\it true} if key is found else returns {\it false}.
-
-    \Function{find}{key, prevRef\&}
-       \State lid := simdINDEX();
-       \State startRef := hashFunction(key);
-       \State prevRef  := startRef;
-       \State doneFlag := false;
-       \While{(!doneFlag)}
-          \If{(lid = 1)}
-             \State delStatus := delMarkedNode(prevRef);
-          \EndIf
-          \State simdBARRIER();
-          \State delStatus = simdBROADCAST(delStatus,1);
-          \If{delStatus = true}
-             \State keyStatus := checkKey(key, prevRef);
-             \If{(keyStatus = NODE\_DELETED)}
-                \State prevRef := startRef;
-             \ElsIf{(keyStatus = KEY\_FOUND)}
-                \State 
-                \Return true
-             \ElsIf{(keyStatus = KEY\_NOT\_FOUND)}
-                \State 
-                \Return false
-             \EndIf
-          \Else
-             \State prevRef := startRef;   
-          \EndIf
-       \EndWhile
-    \EndFunction
-  \end{algorithmic}
-\end{algorithm}
 

### 2015-07-07 Docs/paper.tex
doc changed

@@
   \begin{algorithmic}[1]
-    \Require
-        \Statex startRef:Reference to the starting node.
-    \Ensure
-       \Statex cleans all the logically deleted nodes.
+    %\Require
+    %    \Statex startRef:Reference to the starting node.
+    %\Ensure
+    %   \Statex cleans all the logically deleted nodes.
     \Statex   
@@
       \State index = 0;      
-      \While(true)
+      \While{(true)}
         \State pRef = {\it Null};
@@
 
-\section{Proof of Correctness}
+\begin{algorithm}
+  \caption{clones a node and adds a key to it.}
+  \label{alg:clone}
+  \begin{algorithmic}[1]
+    %\Require
+    %    \Statex startRef:Reference to the starting node.
+    %\Ensure
+    %   \Statex cleans all the logically deleted nodes.
+    \Statex   
+    \Function{clone}{ref, key}
+      \State newRef = ALLOC();
+      \Comment{assumption is that ALLOC always returns a node}
+      \State newRef:next = ref:next;
+      \State keyIndex = simdIndex(ref:val = key);
+      \If{keyIndex = 0}
+        \State minIndex    = min(simdIndex(ref:val = {\it empty}));
+        \Comment{simdIndex returns zero if condition is not met}         
+        \If{(minIndex $\not =$ 0)}
+          \State simdCopy(ref:val, newRef:val);
+          \State newRef:val[minIndex] = key;
+          \State
+          \Return newRef;
+        \Else
+          \State prevNewRef = ALLOC();
+          \State simdCopy(ref:val, prevNewRef:val, (ref:val < key));
+          \State simdCopy(ref:val, newRef:val, (ref:val > key));
+          \State prevNewRef:next = [newRef,[0,0,0]];
+          \State minIndex    = min(simdIndex(newRef:val = {\it empty}));      
+          \State newRef:val[minIndex] = key;
+          \State
+          \Return prevNewRef;
+        \EndIf
+      \Else
+        \State simdCopy(ref:val, newRef:val);
+        \State newRef:val[keyIndex] = {\it empty};
+        \State
+        \Return newRef;
+      \EndIf  
+      \State
+      \Return {\it null};
+    \EndFunction
+  \end{algorithmic}
+\end{algorithm}
 
 \begin{algorithm}
-  \caption{Insert a key in the set}
-  \label{alg:insert}
+  \caption{traverses the list from prev ref to next ref.}
+  \label{alg:traverse}
   \begin{algorithmic}[1]
-    \Require
-       \Statex {\it key} to be searched.
-    \Ensure
-       \Statex Returns {\it false} if key is found else inserts the {\it key}.
+    %\Require
+    %    \Statex startRef:Reference to the starting node.
+    %\Ensure
+    %   \Statex cleans all the logically deleted nodes.
+    \Statex   
+    \Function{traverse}{prevRef, nextRef}
+      \State pRef = prevRef;
+      \State [nRef, pBits] = unpackRef(pRef:next);
+      \While{(pBits = [0,x,x])}
+        \If{(nRef $\not = $ nextRef)}
+          \State pRef = nRef;
+          \State [nRef, pBits] = unpackRef(pRef:next);
+        \Else
+          \State
+          \Return pRef;
+        \EndIf
+      \EndWhile
+      \State
+      \Return {\it null};
+    \EndFunction
+  \end{algorithmic}
+\end{algorithm}
 
+\begin{algorithm}
+  \caption{adds a key to the set.}
+  \label{alg:add}
+  \begin{algorithmic}[1]
+    %\Require
+    %    \Statex startRef:Reference to the starting node.
+    %\Ensure
+    %   \Statex cleans all the logically deleted nodes.
     \Statex   
-    \Function{insert}{key}
-      \State doneFlag := false;
-      \While{(!doneFlag)}
-        \State findStatus := find(key, prevRef);
-        \If{(findStaus = true)}
+    \Function{add}{key}
+      \While{(true)}
+        \State status = FIND(key, prevRef nextRef,index);
+        \If{status = {\it window\_found}}
+          \State pRef = TRAVERSE(prevRef, nextRef);
+          \If{(pRef $\not =$ {\it null})}
+            \State cloneRef = CLONE(nextRef,key);
+            \State status = REPLACE(pRef,cloneRef);
+            \If{(status = {\it replaced})}
               \State
-          \Return false;
+              \Return {\it true};
             \EndIf
-        \State [nextRef, prevMark] = getUnmarkedRef(prevRef);
-        \If{(prevMark = 0)}
-          \State insertStatus = false;
-          \State minIndex := getMinEmptySlot(nextRef,nodePool);
-          \If{(minIndex = 0)} \Comment No empty slot.
-            \State insertStatus := insertNodeAndKey(key, prevRef,nextRef);
-          \ElsIf{(minIndex > 0)}
-            \State insertStatus := insertKey(key, minIndex, prevRef, nextRef);
           \EndIf
-          \If{insertStatus = true}
+        \Else
           \State
-            \Return true;
-          \EndIf
+          \Return {\it false}
         \EndIf
@@
 \begin{algorithm}
-  \caption{Find empty slot with minimum index}
-  \label{alg:minindex}
+  \caption{removes a key from the set.}
+  \label{alg:remove}
   \begin{algorithmic}[1]
-    \Require
-      \Statex {\it nextRef} in which minumum index to empty slot is to be
-              found.
-    \Ensure
-      \Statex Returns {\it -1} if {\it nextRef} is deleted, {\it 0} if no
-              empty slot is found, or minimum index to empty slot.
-
-    \Function{getMinEmptySlot}{nextRef}
-      \State val := nextRef:V[lid];
-      \State indicator := (val = EMPTY\_SLOT)?lid:0;
-      \If {(simdALL(indicator = 0))}
-        \State minIndex := 0;
-      \Else
-        \State minIndex := simdMIN(indicator);
+    %\Require
+    %    \Statex startRef:Reference to the starting node.
+    %\Ensure
+    %   \Statex cleans all the logically deleted nodes.
+    \Statex   
+    \Function{remove}{key}
+      \While{(true)}
+        \State status = FIND(key, prevRef nextRef,index);
+        \If{status = {\it key\_found}}
+          \State pRef = TRAVERSE(prevRef, nextRef);
+          \If{(pRef $\not =$ {\it null})}
+            \State cloneRef = CLONE(nextRef,key);
+            \State status = REPLACE(pRef,cloneRef);
+            \If{(status = {\it replaced})}
+              \State
+              \Return {\it true};
             \EndIf
-      \State [nnRef,nextMark] := getUnmarkedPtr(nextRef);
-      \If{(nextMark = 0)}
-        \State
-        \Return minIndex;
+          \EndIf
         \Else
           \State
-        \Return -1;
-      \EndIf  
-    \EndFunction
-  \end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}
-  \caption{Insert a node and a key}
-  \label{alg:insnodekey}
-  \begin{algorithmic}[1]
-    \Require
-      \Statex {\it key} to be inserted.
-      \Statex {\it prefRef} and {\it nextRef} give window in which new node
-              and key are to be inserted.
-    \Ensure
-       \Statex Returns {\it true} if successful.
-
-    \Function{insertNodeAndKey}{key, prevRef, nextRef}
-      \If{(lid = 1)} 
-        \State newNRef := newNode();
-        \State newNNRef := newNode();
-      \EndIf
-      \State simdBARRIER();
-      \State newNRef  := simdBROADCAST(newNRef,1);
-      \State newNNRef := simdBROADCAST(newNRef,1);
-
-      \State newNRef:next := [newNNRef,0];
-      \If{(nodePool[nextRef]:V[lid] < key)}
-        \State nodePool[newNRef]:V[lid] := nodePool[nextRef]:V[lid];
-        \State nodePool[newNNRef]:V[lid] := EMPTY\_SLOT;
-      \Else
-        \State nodePool[newNNRef]:V[lid] := nodePool[nextRef]:V[lid];
-        \State nodePool[newNPRef]:V[lid] := EMPTY\_SLOT;
-      \EndIf
-      \State minIndex := getMinEmptySlot(newNRef,nodePool);
-      \State nodePool[newNRef]:V[minIndex] := key;
-      \State nodePool[newNNPtr]:next := [nextRef,0];
-      \State status := CAS(nodePool[prevRef]:next,[nextRef,0],newNPtr);
-      \Return status;
-    \EndFunction
-  \end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}
-  \caption{Insert a key in a node}
-  \label{alg:inskey}
-  \begin{algorithmic}[5]  
-    \Function{insertKey}{key, minIndex, nextRef\&, nodePool}
-      \If{lid = 1}
-        \State status := CAS(nodePool[nextRef]:V[minIndex],EMPTY\_SLOT,key);
-      \EndIf
-      \State simdWait();
-      \State status = simdBroadcast(status, 1);
-      \Return status;
-    \EndFunction
-  \end{algorithmic}
-\end{algorithm}
-
-\begin{algorithm}
-  \caption{Delete a key from the set}
-  \label{alg:delkey}
-  \begin{algorithmic}[5]  
-    \Function{remove}{key, nodePool}
-      \State doneFlag := false;
-      \While{(!doneFlag)}
-        \State findStatus := find(key, prevRef\&, nextRef\&, nodePool);
-        \If{(findStaus = false)}
-          \State
-          \Return false;
-        \EndIf
-        \State val   := nodePool[nextRef]:V[lid];
-        \If{(val = key)}
-          \State status := CAS(nodePool[nextRef]:V[lid],key,EMPTY\_SLOT);
-        \EndIf
-        \State simdWait();
-        \State status := simdBrodacast(status);
-        \If{(status = true)}
-          \State status := deleteNode(prevRef\&, nextRef\&, nodePool);
-          \Return status;
-        \Else
-          \State
-          \Return false;
+          \Return {\it false}
         \EndIf
@@
 
-\begin{algorithm}
-  \caption{Delete a node}
-  \label{alg:delnode}
-  \begin{algorithmic}[5]  
-    \Function{deleteNode}{prevRef\&, nextRef\&, nodePool}
-         \State val := nodePool[nextRef]:V[lid];
-         \State status := simdAll(val,EMPTY\_SLOT);
-         \If{(status = true)}
-           \State [nnRef,nextMark] := getPtr(nextRef);
-           \State newMark := 1;
-           \If{(lid = 1)}
-              \State status := CAS(nodePool[nextRef]:next,[nnRef,nextMark],[nnRef,newMark]);
-              \If{(status = true)}
-                \State status = delMarkedNodes(prevRef,NodePool); 
-              \EndIf
-           \EndIf
-           \State simdWait();
-           \State status = simdBroadcast(status,1);
-           \State
-           \Return status;
-         \EndIf
-    \EndFunction
-  \end{algorithmic}
-\end{algorithm}
+%\section{Proof of Correctness}
 
